Nanophotonic Computational Design

### 2013-03-15 paper/paper.tex
Slowly getting there.

% Runtimes for the design process ranged from 8-80 hours 
%     based on the size of the design space.

\subsection{TE mode converter}
Our first result was a mode conversion device operating in the TE polarization,
    which we define as that mode where the primary E-field component
    of the waveguide mode is polarized in the plane of the structure.
Such a device is significant because 
    it demonstrates the feasibility of muli-mode on-chip optical networks
    by showing that high-efficiency mode conversion 
    can readily be achieved in planar on-chip nanophotonic structures.
Furthermore, this device also demonstrates that this can be achieved
    within very small device footprints 
    ($1.6 \times 2.4$ microns for this device in particular).

@@

\myfig{takeaway}
    {Structure and E-field at the central plane of the device.
    The conversion efficiency into the second-order mode is 86.4\%,
    while the power into the rejection mode (fundamental) is 0.7\%.}

\subsection{TM mode converter}

@@

\myfig{wgc_tm}
    {Structure and E-field at the central plane of the device.
    The conversion efficiency into the second-order mode is 76.9\%,
    while the power into the rejection mode (fundamental) is 1.0\%.}

\subsection{Spatial, polarization, and wavelength splitters}
Next, we demonstrate the design of nanophotonic waveguide mode splitters.
Such devices can be used as multiplexors or demultiplexors and
    are the key component in utilizing a single waveguide to transmit 
    multiple optical signals.

@@

>>>>

% Runtimes for the design process ranged from 8-80 hours 
%     based on the size of the design space.
\subsection{Mode converters}
\subsubsection{TE mode converter}
Our first result was a mode conversion device operating in the TE polarization,
    which we define as that mode where the primary E-field component
    of the waveguide mode is polarized in the plane of the structure.
Such a device is significant because 
    it demonstrates the feasibility of muli-mode on-chip optical networks
    by showing that high-efficiency mode conversion 
    can readily be achieved in planar on-chip nanophotonic structures.
Furthermore, this device also demonstrates that this can be achieved
    within very small device footprints 
    ($1.6 \times 2.4$ microns for this device in particular).

@@

\myfig{takeaway}
    {Structure and E-field at the central plane of the device.
    The conversion efficiency into the second-order mode is 86.4\%,
    while the power into the rejection mode (fundamental) is 0.7\%.
    Device footprint is $1.6\times2.4$ microns.}

\subsubsection{TM mode converter}

@@

\myfig{wgc_tm}
    {Structure and E-field at the central plane of the device.
    The conversion efficiency into the second-order mode is 76.9\%,
    while the power into the rejection mode (fundamental) is 1.0\%.
    Device footprint is $1.6\times2.4$ microns.}

\subsection{Splitters}
Next, we demonstrate the design of nanophotonic waveguide mode splitters.
Such devices can be used as multiplexors or demultiplexors and
    are the key component in utilizing a single waveguide to transmit 
    multiple optical signals.

@@

The performance specification for each device is simply to convert
    90\% of the input power in a particular input mode into
    either one of the output modes.
At the same time, we specify that the transmission into the other output mode 
    be kept below 1\% of input power.

\subsubsection{Spatial mode splitter}
We demonstrate what is, to our knowledge, 
    the first design for a three-dimensional
    nanophotonic spatial mode splitter.
Such a device is the key enabler for multi-mode on-chip optical circuits,
    and we show here that they can be designed to be highly efficient
    while utilizing a very small device footprint ($2.8\times2.8$ microns). 
The performance specification is shown in \fig{3Db_spl_modal},
    and the final results is shown in \fig{spl_modal}.

\myfig{3Db_spl_modal}
    {Input mode is either the fundamental or second-order
        TE-polarized mode on the left.
    Output modes are the fundamental waveguide modes of either output 
        waveguide on the right.
    Output power into the desired output arm is specified to be greater than 90\%,
        while power into the opposing arm is set to below 1\%.}
\myfig{spl_modal}
    {The conversion efficiencies into the upper and lower output arms
        are 88.7\% and 77.4\% respectively, 
        while the rejection powers for the same modes are 0.27\% and 0.20\%.
    Device footprint is $2.8\times2.8$ microns.}

\subsubsection{TE/TM splitter}
In addition to splitting different spatial modes, 
    we show that different polarization can also be split.
\Fig{3Db_spl_tetm} shows the performance specification of a 
    device which is able to separate fundamental TE- and TM-polarized
    waveguide modes into separate arms.
The final, verified result is shown in \fig{spl_tetm}.

Not only is this result the first of its kind,
    it is the first in the device category where a single device
    is able to control both polarizations within the same device footprint.
This shows the versatility and broad applicability of our method.

\myfig{3Db_spl_tetm}
    {Input mode is either the fundamental TE- or TM-polarized 
        mode on the left.
    Output power into the desired output arm is specified to be greater than 90\%,
        while power into the opposing arm is set to below 1\%.}
\myfig{spl_tetm}
    {The conversion efficiencies into the upper and lower output arms
        are 87.6\% and 88.8\% respectively, 
        while the rejection powers for the same modes are 1.06\% and 0.58\%.
    Device footprint is $2.8\times2.8$ microns.}

\subsubsection{Wavelength splitter}
Traditional wavelength splitting devices can also be designed using our method.
Here, we show that the 1550 nm and 1310 nm wavelengths can be split
    in a very small device footprint ($2.8\times2.8$ microns).
\myfig{3Db_spl_wdm}
    {Input mode is the fundamental TE-polarized mode on the left at 
        a wavelength of either 1550 nm or 1330 nm.
    Output modes are the fundamental waveguide modes of either output 
        waveguide on the right.
    Output power into the desired output arm is specified to be greater than 90\%,
        while power into the opposing arm is set to below 1\%.}
\myfig{spl_wdm}
    {The conversion efficiencies into the upper and lower output arms
        are 83.2\% and 78.7\% respectively, 
        while the rejection powers for the same modes are 0.49\% and 1.66\%.
    Device footprint is $2.8\times2.8$ microns.}
